Solution of Differential Algebraic Equations with Manifold Constraints on the Latent Space of an Autoencoder

### 2019-05-17 paper/paper.tex
More writing about the paper

\begin{align}
\text{Solve for}\, \rho(t), \, h(t), \, p(t),\, \text{and}\, T(t)\, \text{satisfying:}\\
\partial_t \rho & = \nabla \cdot \mathbf{k}\nabla p + r\\
\partial_t \rho h - p & = \nabla \cdot \mathbf{k'}\nabla T + s\\
\text{such that they lie on the material EOS,}\\
EOS(\rho,h,p,T) & = 0
\end{align}

@@

We'll use the autoencoder to generate the parameterization of \(x(q)\)
and \(y(q)\). By the chain rule, the velocities are related to the
feature space by

\begin{equation}
\dot{x} = \frac{\mathrm{d}x(q)}{\mathrm{d}t} = \frac{\partial x}{\partial q}\frac{\mathrm{d}q}{\mathrm{d}t}
\end{equation}

and similarly for the \(y\) direction.

Taking the partial derivatives with respect to the feature variable and
its rate, the components to the equation of motion are

\begin{equation}
\frac{\partial L}{\partial q} = m g \frac{\partial y}{\partial q}
\end{equation}

When we want to solve the dynamics, we can treat the autoencoder the
same as \(x(\theta)\), plugging in

\[L(x(q),v(q,\dot{q}))\]

and build the DAE we know from physics:

\[\frac{\mathrm{d}}{\mathrm{d}t}\frac{\partial L}{\partial \dot{q}} = \frac{\partial L}{\partial q}\]

where we get the velocity with the chain rule:

\[v = \frac{\partial x}{\partial q} \dot{q}\]

Then plug it into a Runge Kutta (trapezoidal) to solve with Newton's
method:

\[\frac{\partial L}{\partial \dot{q}}_i - \Delta t \frac{\partial L}{\partial q}_i = \frac{\partial L}{\partial \dot{q}}_0 + \Delta t \frac{\partial L}{\partial q}_0\]

>>>>

\begin{align}
\text{Solve for}\, \rho(t), \, h(t), \, p(t),\, \text{and}\, T(t)\, \text{satisfying:}\\
\partial_t \rho &  = \mathbf{k}_p(p_\infty - p) + r\\
\partial_t (\rho h-p) & = \mathbf{k}_T(T_\infty-T) + s \\
\text{such that they lie on the material EOS,}\\
\rho,h,p,T & \in \{\text{EOS}\}
\end{align}

@@

We'll use the autoencoder to generate the parameterization of \(x(q)\)
and \(y(q)\). By the chain rule, the velocities are related to the
feature space by
\begin{equation}
\dot{x} = \frac{\mathrm{d}x(q)}{\mathrm{d}t} = \frac{\partial x}{\partial q}\frac{\mathrm{d}q}{\mathrm{d}t}
\end{equation}
and similarly for the \(y\) direction.

When we want to solve the dynamics, we can treat the autoencoder the
same as \(x(\theta)\), plugging in
\[L(x(q),v(q,\dot{q}))\]
Taking the partial derivatives with respect to the feature variable and
its rate, the components to the equation of motion are build the DAE we know from physics:

\[\frac{\mathrm{d}}{\mathrm{d}t}\frac{\partial L}{\partial \dot{q}} = \frac{\partial L}{\partial q}\]
where we get the velocity with the chain rule:
\[v = \frac{\partial x}{\partial q} \dot{q}\]

Then plug it into a Runge Kutta (trapezoidal) to solve with Newton's
method:
\[\frac{\partial L}{\partial \dot{q}}_i - \Delta t \frac{\partial L}{\partial q}_i = \frac{\partial L}{\partial \dot{q}}_0 + \Delta t \frac{\partial L}{\partial q}_0\]
